### 2021-04-04 newvariant.tex
bias and sleep

We can assess these biases by plotting the estimated strength of the variant $\hat{\RR}_{\textrm{var}}(t)$ against the estimated strength of the wild type $\hat{\RR}_{\textrm{wt}}(t)$ (\fref{Rtbias}C,F,I).
When generation-interval distributions are correctly specified, we obtain a straight line with a slope of $\rho$ and intercept at zero (\fref{Rtbias}C).
When the assumed mean generation interval is longer (or shorter) than the that of the variant, we over-estimate (or under-estimate) the slope (\fref{Rtbias}H,L).
Smooth changes in $\RR$ generate circular patterns but biases in slopes are clear.

>>>>

We can also assess these biases by plotting the estimated strength of the variant $\hat{\RR}_{\textrm{var}}(t)$ against the estimated strength of the wild type $\hat{\RR}_{\textrm{wt}}(t)$ (\fref{Rtbias}C,F,I).
When generation-interval distributions are correctly specified, we obtain a straight line with a slope of $\rho$ and intercept at zero (\fref{Rtbias}C).
When the assumed mean generation interval is longer (or shorter) than the that of the variant, we over-estimate (or under-estimate) the slope (\fref{Rtbias}H,L).
In addition, the intercept (if we were to perform regression) need not be at zero due to biases in the slope.
Smooth changes in $\RR$ further generate circular patterns but biases in slopes are clear.
